\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amsmath}
\geometry{margin=2.2cm}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\title{Krogh GUI\\Quickstart and Practical Workflow Guide}
\author{Practical reference}
\date{23 April 2026}

\begin{document}
\sloppy
\maketitle
\tableofcontents

\section{Purpose}
This quickstart explains how to use the current Krogh GUI version efficiently in daily work. It is focused on operations, while the full mathematical derivations are documented in \texttt{krogh\_GUI\_documentation.pdf} and \texttt{oxygenation\_diagnostic\_mvp\_documentation.pdf}.

\section{Start the application}
From the project root:
\begin{verbatim}
source .venv/bin/activate
python app.py
\end{verbatim}

\section{Project orientation (short)}
You will mainly interact with:
\begin{itemize}
    \item \texttt{app.py} (launcher),
    \item \texttt{krogh\_GUI.py} (main GUI and forward model),
    \item \texttt{krogh\_app/reconstruction.py} (inverse fitting),
    \item \texttt{oxygenation\_diagnostic\_mvp.py} (probabilistic diagnostics),
    \item \texttt{krogh\_app/persistence.py} (report and export logic).
\end{itemize}

\section{GUI overview}
Main tabs:
\begin{itemize}
    \item \textbf{Inputs}: single-case physiological setup.
    \item \textbf{Series}: 1D/2D parameter sweeps and plots.
    \item \textbf{Numerics}: solver tolerances/iterations and bootstrap sample count.
    \item \textbf{Diagnostic}: probabilistic assessment, reconstruction, report export, benchmark button.
\end{itemize}

\section{Single-case workflow}
\begin{enumerate}
    \item Enter PO$_2$ inlet, mitoP50, pH, pCO$_2$, temperature, perfusion factor, relative tissue O$_2$ consumption, and base tissue radius.
    \item Keep axial diffusion enabled unless you intentionally want a faster reduced run.
    \item Set absolute and relative high-PO$_2$ thresholds if needed.
    \item Click \texttt{Run}.
\end{enumerate}

Key outputs:
\begin{itemize}
    \item \texttt{P\_venous}, \texttt{P\_tissue\_min}, \texttt{P\_tissue\_p05},
    \item hypoxic fractions below 1/5/10 mmHg,
    \item above-threshold fractions (absolute and relative),
    \item sensor-like tissue average PO$_2$, arterial and venous saturation.
\end{itemize}

\section{Series workflow}
\begin{enumerate}
    \item Select 1D or 2D sweep.
    \item Choose primary (and optional secondary) sweep parameter; metabolic-rate sweeps are supported.
    \item Set start/end/step values.
    \item Select plot fields and plot mode (2D, 3D surface, heatmap).
    \item Run series and optionally save run bundle.
\end{enumerate}

Saved bundle contents:
\begin{itemize}
    \item \texttt{series\_results.xlsx} (or CSV fallback),
    \item \texttt{series\_setup} sheet/file,
    \item plot PNG files,
    \item \texttt{run\_parameters.txt}.
\end{itemize}

\section{Numerics workflow}
Use the \texttt{Numerics} tab when stability or precision is critical.

Most important controls:
\begin{itemize}
    \item ODE tolerances: \texttt{ode\_rtol}, \texttt{ode\_atol},
    \item ODE max step: \texttt{ode\_max\_step},
    \item tissue iteration limits/tolerances,
    \item coupling iteration limits/tolerances,
    \item \texttt{bootstrap\_samples} for reconstruction uncertainty.
\end{itemize}

Practical rule: tighten tolerances for extreme physiology, sharp sweep transitions, or publication figures.

\section{Diagnostic and reconstruction workflow}
\begin{enumerate}
    \item Enter blood-gas and sensor values in \texttt{Diagnostic} tab.
    \item Click \texttt{Run diagnostic}.
    \item Review state probabilities, alert level, risk score, and dominant drivers.
    \item Click \texttt{Reconstruct Krogh Cylinder} to fit perfusion/mitoP50/metabolic factor while using the currently selected base tissue radius for the primary geometry.
    \item Review hidden hypoxic burden and radius sensitivity (30/50/100 \textmu m).
\end{enumerate}

Additional options:
\begin{itemize}
    \item radius mode: all variants or selected radius only,
    \item auto-save independent 30/50/100 \textmu m reconstructions to \texttt{Diagnostic reports}.
\end{itemize}

\section{Report and export workflow}
\subsection{Diagnostic report export}
Button: \texttt{Save diagnostic report}.

Formats: JSON or CSV.

Contains: input values, diagnostic outputs, reconstruction payload fields, uncertainty and burden fields.

\subsection{Publication report export}
Button: \texttt{Save English publication report}.

Formats: TXT, TEX, or PDF.

PDF notes:
\begin{itemize}
    \item requires \texttt{pdflatex} in PATH,
    \item if figure(s) exist, report can embed reconstruction images,
    \item intermediate TEX is written automatically for PDF generation.
\end{itemize}

\section{Command-line validation and benchmark tools}
\subsection{Synthetic validation}
\begin{verbatim}
source .venv/bin/activate
python run_synthetic_validation.py
\end{verbatim}
Outputs in \texttt{Diagnostic reports/}:
\begin{itemize}
    \item \texttt{synthetic\_validation\_report.csv/json},
    \item \texttt{synthetic\_validation\_trend\_checks.csv/json},
    \item \texttt{synthetic\_validation\_robustness.csv/json}.
\end{itemize}

\subsection{Reconstruction benchmark}
\begin{verbatim}
source .venv/bin/activate
python run_reconstruction_benchmark.py
\end{verbatim}
Outputs in \texttt{Diagnostic reports/}:
\begin{itemize}
    \item \texttt{reconstruction\_benchmark.csv/json},
    \item \texttt{reconstruction\_benchmark\_comparison.csv/json}.
\end{itemize}

\section{Interpreting results safely}
\begin{itemize}
    \item Do not interpret alert color alone; include confidence, certainty, and dominant drivers.
    \item For reconstruction, review fit warning, boundary hit, uncertainty width, and radius sensitivity.
    \item Use trends and repeated measurements whenever possible.
\end{itemize}

\section{When to open the full manuals}
Use detailed manuals when you need:
\begin{itemize}
    \item complete equations and solver derivations,
    \item function-level call mapping and parameter tracing,
    \item precise reconstruction algorithm details,
    \item detailed output schema and reporting internals.
\end{itemize}

\end{document}
